Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-29 journal/article.tex
Work in progress

As the organization is changing it is necessary that people know what to change
into. Therefore the majority of cases described the use of training in the
transformation.

@@

Management was also among the first ones to receive agile training, and they
received more in-depth training than the rest of the organization [P11].

>>>>

As the organization is changing it is necessary to train people so they get some
familiarity with the new model that is being pursued. The majority of cases
described the use of training in the transformation.

@@

Management was also among the first ones to receive agile training. In some
cases management received more in-depth training than the rest of the
organization [P11].
